---
title: "Text Analyis & Bash"
pagetitle: "Text Analysis & Bash"
---

```{r echo=FALSE}
knitr::read_chunk("./scripts/workshop_files.R")
```

## Description

This workshop will briefly introduce:

* core concepts in text analysis.
* basic computational approaches to text analysis.
* command line tools for basic text analysis.

## Objectives

* Introduce core techniques used in text analysis.
* Review the automated vs computer assisted approaches to text analysis.
* Introduce Linux command line tools for text analysis.

## Outcomes

* Know what questions to ask when tackling a text analysis question.
* Describe core concepts used in text analysis.
* Run basic text queries on a document using Linux command line tools.

## What you will need

* A computer. Neither a tablet nor cell phone will suffice.

## Pre-load

* Set up a terminal
     - Mac and Linux: bash or zsh terminal apps are already installed, simply go to your app library.
     - Windows: install Git, which will include the Git Bash utility. From the start menu, type `bash` to launch the application.

## Files

```{r loadfiles, results='asis', echo=FALSE}
```
